\documentclass[a4paper, 12pt, openany, oneside]{book}
\input{inc/Header.tex} % Included packages located in a separate file
\pagestyle{plain} %Page numbers on the bottom

\begin{document}

% Front page
%\pagestyle{emty} %No numbers
%\input{000_TitlePage.tex}
%\cleardoublepage

% Table of Contents
%\newpage
%\pagenumbering{roman}
%\tableofcontents

% Main Chapters
\newpage
\pagestyle{plain}
\pagenumbering{arabic}
% Abstract
%\input{010_Introduction.tex} % Intro & Motivation (Open areas proposed in the literatures)
\chapter{Introduction}
Presentation of the project.

Current state[60\%].
Goals:-

\section{Human activity Analysis}
Justification of the problem and how this is linked to robotics.
At the same time, these should be linked to the project (ASP).
This is the route from the general problem to my project, described in general here, but with more detail in the next chapter.
Current state[90\%].
Goals: -


\subsection{Test case: ``The library scenario''}
Presentation of the test scenario.
An example is needed here, to introduce an example that the proposed approach can treat.

Current state[70\%].
Goals: Put the problem example here.


\section{Methodology}
The presentation of the project, i.e. proposal in general.

Current state[10\%].
Goals: Present the project. What kind of techniques are going to be used? Why?


\subsection{System presentation}
Structure of the system.
How all parts assemble together.

Current state[10\%].
Goals: Describe in general the project and what kind of system is being proposed. Some proposed experiments.


\subsection{Outcome}
The scope of the project.
Expected challenges and outcome.
Evaluation.


Current state[10\%].
Goals: What challenges and results are expected.


\subsection{Outline}
Outline for the rest of the document (this could be done wwith the structure of the document).


%\input{020_RelatedWork.tex} % "Related Work" Literature rev (separated areas, in my case AR + ASP + KRR(incomplete) + Semantic Map)
\chapter{Related Work}

Current state[90\%].
Goals: Last section (discussion), I think is needed to link my project in the literature review.


\section{General antecedents - Perception in AI}
This is are the main branches where the problem come from (how has been studied) and especially, from a CS point of view.

\section{Activity Recognition} 
Presentation of the taxonomy of the problem. 
How has been treated before.
What techniques have been used.
The taxonomy is built upon the representation and techniques used.

\subsection{Single-layered approaches}
Analysis of low level actions (usually atomic ones).
\subsubsection{Continuous approaches} % BEFORE: Space-Time approaches
\subsubsection{Sequential approaches} %TODO Go deeper.

\subsection{Hierarchical approaches}
High level activity recognition (symbolic and statistical).
\subsubsection{Statistical}
\subsubsection{Syntactic}
\subsubsection{Description-based} \label{sec_description_ap}

\section{Description-based activity recognition and mobile robotics}
This is the main branch where this project fits.
I go in detail with the techniques that I'm looking at.
I also try to establish the link with robotics.

\subsection{Description-based activity recognition}

\subsubsection{Activity recognition from a robotics perspective}
Previous works in robotics, some that serve as example of the progress, used approaches in the area and uncovers the open problems.

\section{Answer Set Programming} % Because is one of the main contributions, I put it appart.
As this is an important part of my thesis, I present it here in general

\subsection{ASP as a declarative problem solving technique}
What kind of problems can be treated with ASP.
How does it work.
How problems are modeled with ASP.

\subsection{ASP as a knowledge representation language}
Link ASP to knowledge representation.
Some pros & cons, and challenges ahead

\subsubsection{ASP implementations}
Present popular systems around (potassco & DLV).

\subsection{ASP and robotics}
% University of Sabanci
Link ASP with robotics.
R-Sabanci University.
R-Potsdam University.

\section{Discussion}
Conclusions about the state of the art.
What is missing, and how my project fits there.

%\section{Semantic Mapping}



%\input{030_ResearchProblem.tex} % (Mike --> Model & Methodology) % Research Problem (Analysis) (Problem Definition -> Rafee)
\chapter{Research Problem}
Current state[50\%].
Goals:-

Present the problem, the one for this project.

\section{Description}
Current state[50\%].
Goals: Need to go to the point and connect it with the library example.

Use the library case, the example.
What kind activities are going to be solved?
What kind of data are we inderested in?


\section{Methodology}
Current state[50\%].
Goals: Reuse the diagram from the first chapter and develop it.

What kind of system is going to be used (proposed)?
What do I already have in hand?
What is missing?


\section{Evaluation}
Current state[20\%].
Goals:-

What kind of challenges are expected?
What is the strategy for them?

What kind of outcomes are expected?


\chapter{Work Plan}
Current state[0\%].
Goals: Present the parts of the problem  and how are they going to be assembled. This is the first goal. Then I need target simple test examples. Then focus on improvements. Set goals (e.g. present work).

What's the next step for this project?

Put yourself some goals.

\section{Short term (6 months - 1 year)}
\section{Long term}
\section{Timetable}

\end{document}
