\documentclass[a4paper, 12pt, openany, oneside]{book}
\input{inc/Header.tex} % Included packages located in a separate file
\pagestyle{plain} %Page numbers on the bottom

\begin{document}

% Front page
\pagestyle{emty} %No numbers
\input{000_TitlePage.tex}
\cleardoublepage

% Table of Contents
\newpage
\pagenumbering{roman}
\tableofcontents

% Main Chapters
\newpage
\pagestyle{plain}
\pagenumbering{arabic}
% Abstract
%\input{010_Introduction.tex} % Intro & Motivation (Open areas proposed in the literatures)
% Outcome
%\input{020_RelatedWork.tex} % "Related Work" Literature rev (separated areas, in my case AR + ASP + KRR(incomplete) + Semantic Map)

%================================================
%================================================
%================================================
\chapter{Related Work}

% 0 - GENERALITIES
% Perception
% Symbol ground
% Anchoring
% Frame Problem

\section{Activity recognition}

Activity recognition is an important research area in the context of automated perception. 
It has many applications as surveillance, inspection, verification, generation of automated reports, etc. 
The main goal is to automatically analyse the ongoing activities from an unknown sensory source (a video sequence in most of the cases).
Activities play a relevant role in the interpretation of a scene, not only in physical terms, but also symbolically as they can usually be associated with a meaning or an interpretation.

The problem has been studied first in psychology. In \citep{Heider1944_Experimental}, an animation film was created using only polygons to demonstrate how the motion of abstract entities can be interpreted by a human observer.

The problem has been studied in AI from different areas, principally in computer vision or as a knowledge processing problem. 
Early work in computer vision can be traced back to the 1960-70s, as part of the effort to mimic human-like intelligence using visual perception components. In \citet{Johansson1973_VisualPer} locomotion of living organisms is studied using visual marks and then describes a study on interpretation of motion using visual dot markers mounted on a moving body, the patterns are described numerically, but also




The main difference between computer vision and image processing was a desire to recover the three-dimensional structure of the world from images, and to use this as a stepping stone towards full scene understanding \citep{Winston1975_PsyCV}. 


In the early 1970s, simple motion patterns of dots were studied to describe and recognize complex motion patterns (e.g. walking, shaking hands), \citep{Johansson1973_VisualPer}. 
Object recognition was treated in \citep{Barrow1971_RelatDesc} by decomposing an image in regions and describe the relations between them. 
Finally, in this decade, the \textit{block's world} problem was proposed as a test scenario for artificial intelligent systems, particularly regarding planning, knowledge representation and reasoning. 
One important characteristic of the problem is the requirement of a symbolic scene representation to do some reasoning. 
The block's world was also used with physical systems as the robot \textit{Shakey}, \citep{Nilsson84_Shakey}.





% COMPLETE - AR approaches (CV & KRR)
In the context of Artificial Intelligence it has been treated as a Computer Visioandverification, in aabout the problem of interpretation and understanding of a scene from sensory information and also using domain knowledge. 
It is mostly a perceptual action, however reasoning plays an important role too.

% Check the surveys to get the whole image



% 1 - ACTIVITY RECOGNITION PROBLEM
% Historic origins
% Approaches (camera, wearable device, ubiquitous computing)
% Main branches (single layer, multpiple layer)
% Hierarchical approaches

% 1.5 ACTIVITY RECOGNITION WITH A MOBILE ROBOT
A robot can be roughly conceived as a physical entity capable of sensing and performing actions in the world.
With this in mind, it seems clear that a robot, with sufficient sensing capabilities, is a good candidate to perform the task.


% 2 - ANSWER SET PROGRAMMING
% General background
% Related work to AR


% 3 - ASP + Robots -> ROSoClingo
% 
%================================================
%================================================
%================================================


%\input{030_ResearchProblem.tex} % (Mike --> Model & Methodology) % Research Problem (Analysis) (Problem Definition -> Rafee)
%\input{040_Methodology.tex}% * Methodology (Here goes the strategy to face the problem, THE PROPOSAL!!)
%\input{050_Evaluation.tex}% Evaluation (Pros + Cons, Possible failures, etc.)
%\input{060_WorkPlan.tex}% * Work Plan (Research Goals+- --> Paul Engelfield)
% Work Done (so far)
% Timetable

% MAke a Timeline of AR
% Check "Paul Engelfield" --> Good Report

% *5min sketch of the report at the begining

% Bibliography
\clearpage
\bibliographystyle{abbrvnat}
\bibliography{/home/kilgore/Dropbox/Public/Docs/mabp_bibliography.bib}
%\bibliography{Bibliography.bib}


\end{document}
